Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-02-02 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: updated figures with the latests samples

Also,
%
\begin{equation}
\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
= \left[
\frac{\ell c^2 (1 + z)}{G M}
\right]^{p}
\end{equation}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
\caption{Preliminary plot.}
\label{fig:dCS_bounds}
\end{figure}

>>>>

Also,
%
\begin{equation}
\gamma
%
= \frac{\ell^{p}}{M_{\rm s}^{p}}
%
% = \frac{\ell^{p} (1 + z)^{p}}{M^{p}}
%
= \left[
\frac{\ell c^2 (1 + z)}{G M}
\right]^{p}
\label{eq:def_gamma}
\end{equation}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
\caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
The posterior shows that information was gained on this parameter relative to
the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
%
The vertical lines represent two threshold for the validity of the theory as
an EFT.
%
The dotted line (labelled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
given by the median value of the secondary's mass $\epsilon \, (G m_2 / c^2)$.
%
The dot-dashed line (labelled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
given by the median value of the remnant's mass $\epsilon \, (G M_{f} / c^2)$.
%
For both, we used $\epsilon = 0.5$.
%
If we take the latter as a lengthscale for the validity of dCS as an EFT, we
have place upper bound on $\ell_{\rm CS} \leqslant 43.8$, within the
approximation of our formalism.
}
\label{fig:dCS_bounds}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
\caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
}
\label{fig:dCS_gamma_plot}
\end{figure}
